### 2021-03-16 README.Rmd
remove non-applicable info from README, now that this is no longer a package.

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) 
[![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/run-tests/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions)

@@

> Authors, (YYYY). *`r Title`*. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). *`r Title`*. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

## Contents

The **R** directory contains functions used in the analysis.

The **analysis** directory contains:

-   [:file\_folder: wrangling](/analysis/wrangling): .R and .Rmd files with code related to data wrangling (i.e. converting raw data into cleaned data)
-   [:file\_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)
-   [:file\_folder: data](/analysis/data): Data used in the analysis.
-   [:file\_folder: figures](/analysis/figures): Plots and other illustrations
-   [:file\_folder: supplementary-materials](/analysis/supplementary-materials): Supplementary materials including notes and other documents prepared and collected during the analysis.

@@

-   open the `.Rproj` file in RStudio
-   run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file).
-   finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

@@

**Text and figures :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) <!-- [![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/R-CMD-check/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions) -->

@@

> Authors, (YYYY).
> *`r Title`*.
> Name of journal/book <https://doi.org/xxx/xxx>

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). *`r Title`*. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

@@

> Authors, (`r format(Sys.Date(), "%Y")`).
> *Compendium of R code and data for `r Title`*.
> Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/xxx/xxx>

@@

-   open the `.Rproj` file in RStudio
-   something about `renv`
-   something about `targets::tar_make()` and `targets::tar_visnetwork()` <!-- -   run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). --> <!-- -   finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console -->

@@

<!-- **Text and figures :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) -->

<!-- <!-- **Code :** See the [DESCRIPTION](DESCRIPTION) file -->

<!-- **Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse -->
